Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-01 paper/sec-analysis.tex
Work on paper

{\bf needs flow chart}

@@

  In addition to the basic $p_T$ and $\eta$
  selection requirements, large-$R$ jets should also
  satisfy the  BDRS mass-drop tagger~\cite{Butterworth:2008iy}
  conditions, in order
  to enhance the discrimination of the signal over the background
  events.
  %
  For the BDRS mass-drop tagger, we use the {\tt FastJet} default
  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.

@@

In Table~\ref{sec:categorisation} we summarize the definitions of each
category

The di-Higgs system is reconstructed by considering all possibilities of forming two pairs of jets with invariant masses $m_{j1j2}$ and 
$m_{j3j4}$, respectively, and choosing the configuration that minimizes their difference $|m_{j1j2} - m_{j3j4}|$. Only the four leading-$p_T$ jets
are considered here.

The boosted selection requires the presence of at least two $bb$-tagged, selected anti-$k_T$ $R=1.0$ jets which are taken as the two Higgs boson candidates.

The intermediate topology requires the presence of at least one $bb$-tagged, selected anti-$k_T$ $R = 1.0$ jet. If there is more than one, the leading one is taken as the first Higgs boson candidate. In addition, there must be at least two anti-$k_T$ $R=0.4$ jets with a separation $\Delta R > 1.0$ with respect to the large-$R$ jet
that is selected as a Higgs boson candidate. The second Higgs boson candidate is reconstructed from the two small-$R$ jets that minimize the difference $|m_{fj} - m_{j1j2}|$.

The resolved selection requires the presence of at least four $b$-tagged, selected anti-$k_T$ $R=0.4$ jets.

All Higgs candidates are required to meet the following Higgs mass window cut: $|m_{H} - 125| < 40$~GeV

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \small
  \begin{tabular}{c|c|c|c}
    \hline
    &  Boosted  &  Intermediate  &  Resolved  \\
    \hline
    \hline 
    Jets  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
    jets  &  $\ge$ 4 small-$R$ jets \\
    Cuts on jets  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
    &  $p_T \ge 40$ GeV \\
    &  & $p_T \ge 40$ GeV (small-$R$ jets)   &    \\
    &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\
    \hline
    \end{tabular}
  \caption{\small Definition of the three event categories used in this
    work, together with the corresponding basic kinematical cuts.
\label{sec:categorisation}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Describe the 3 different kinematic regimes: resolved, semi-boosted and boosted and selection cuts. Show table with numbers. How often do events end up in these categories.

Table 1: how many events we see from Signal and background in each category. Indicate also the overlap between the categories. This table should have also the S/B and S/sqrtB numbers. We need also the S/B and S/sqrtB numbers without the 2b2j and 4j backgrounds in order to compare with the UCL paper in this table.

Figure 1: Higgs pt, eta distributions

Figure 2: b-jet pt distributions

Figure 3: delta R distributions

Figure 4: mass distributions

Table 2: S/B and S/sqrtB table with
All these figures should have the backgrounds overlaid.

This section would show that the 2b2j and 4j backgrounds are important and that control of the fakes is necessary.

This section should also identify which of the different regimes is the most important for the measurement.

>>>>

@@

  In addition to the basic $p_T$ and $\eta$
  selection requirements, large-$R$ jets should also
  satisfy the  BDRS mass-drop tagger~\cite{Butterworth:2008iy}
  conditions, in order
  to enhance the discrimination of the signal over the background
  events.
  %
  For the BDRS mass-drop tagger, we use the {\tt FastJet} default
  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
  %
  Before the mass-drop tagger is applied, the large-$R$ jet
  constituents are reclustered with the Cambridge/Aachen
  algorithm.

@@

After having introduced the types of jet reconstruction
that we will use, as well as the $b$-tagging strategy,
we need to discuss the analysis strategy, including
the event categorization and the cut flow.

The basic idea of this work is the same as in Ref.~\cite{Gouzevitch:2013qca}:
rather than selecting only a specific event topology, such as boosted
or resolved, we aim to consistently combine the information from
the three possible event topologies: boosted, intermediate and
resolved, which we define now.
%
An important difference as compared to~\cite{Gouzevitch:2013qca}
is that here each category is optimised separately, and then
a exclusive categorisation is defined starting from the topology
where the signal significance is the largest.

Let us therefore define the three event categories that
we use in this work:
\begin{itemize}
\item {\it Boosted category}.

  A given event is assigned to the boosted category if it
  contains at least two large-$R$ jets, defined as above,
  and of the tow leading large-$R$ jets have been double-$b$-tagged.
  %
 Therefore, each of these two large-$R$ $b$-tagged jets correspond to the
 decay products of one Higgs boson candidate.

\item {\it Intermediate category}.

  An event is assigned to the intermediate category if
  at least one large $R$ $b$-tagged jet is present.
  %
  If more than one is found, then the leading large-$R$ jet
  is assigned to be the first Higgs candidate.
  %
  In addition, we require at least two small-$R$ jets,
  which must be separated with respect to the large-$R$
  jet by at least an angular separation of $\Delta R\ge 1.0$.
  %
  The small-$R$ jets must be $b$-tagged as well.
  %
  Then, the second Higgs boson candidate is reconstructed
  by selecting the two small-$R$ jets that minimize the difference
  between the invariant mass of the large-$R$ jet, $m_{lR}$,
  with the invariant mass of the sum of the two small-$R$ jets,
  $m_{sR_1+sR_2}$, that is, ${\rm min}\lp m_{lR} -
  m_{sR_1+sR_2}\rp$.

\item {\it Resolved category}.

  Finally, let us define the resolved category.
  %
  An event is assigned to this category
  if at least
  four $b$-tagged small-$R$ jets are present.
  %
  The two Higgs candidates are then reconstructed out of the
  leading four small-$R$ jets in the event
  by considering all possibilities of forming two pairs of jets
  with invariant masses $m_{sR_1+sR_2}$ and 
$m_{sR_3+sR_4}$, respectively, and choosing the configuration that minimizes their difference $|m_{sR_1+sR_2} - m_{sR_3+sR_4}|$. 
  %
  The requirement of restricting this selection to only the four
  leading small-$R$ jets arises from the need to reducing the
  combinatorics from the fakes.
\end{itemize}

In addition, events from each category need to satisfy the usual
Higgs mass window cut, defined by
the following condition
\be
|m_{h,j} - 125| < 40~{\rm GeV} \, , j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of the two Higgs candidates
reconstructed as explained above.
%
We note that this cut is substantially looser as the corresponding
cut used in the ATLAS and CMS $h\to b\bar{b}$ analysis: the motivation
for this is that the MVA will take care of the optimisation of each cut.

In Table~\ref{sec:categorisation} we summarize the definitions of each
category.
%
We emphasize that each category is not exclusive of the others,
and in general there can be a substantial overlap
between the different categories.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \small
  \begin{tabular}{c|c|c|c}
    \hline
    &  Boosted  &  Intermediate  &  Resolved  \\
    \hline
    \hline 
    Jet selection  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
    jets  &  $\ge$ 4 small-$R$ jets \\
    \hline
    Jet cuts  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
    &  $p_T \ge 40$ GeV \\
    &  & $p_T \ge 40$ GeV (small-$R$ jets)   &    \\
    &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\
    \hline
    $b$-tagging  & 2 double-$b$-tags  & 1 double-$b$-tag & 4 single-$b$-tags \\
      &  & and 2 single-$b$-tags  &  \\
    \hline
    \end{tabular}
  \caption{\small Definition of the three event categories used in this
    work, together with the corresponding basic kinematical cuts.
\label{sec:categorisation}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We now justify some of the cuts that we are using.
%
As mentioned before, the cuts in each category are separately
optimised in an inclusive analysis: it is only we have determined
which is the dominant category that the analysis is made exclusive.
%
We begin with the boosted category.
%
In Fig.~\ref{fig:cutplots1} we show
the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/pt_H0_res_C1_boost.pdf}
\caption{\small Left plot: the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.
}
\label{fig:cutplots1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-01 paper/sec-mcsamples.tex
Work on paper

Samples!!!!

>>>>

We consider all the relevant samples that can lead to the event
being tagged as a $HH\to 4b$ candidate.
%
First of all QCD $4b$ multi-jet production of course.
%
But also we generate QCD $2b2j$ and $4j$ multi-jet samples,
that can lead to the even being tagged in the case of multiple light
jets being mistagged as $b$-quarks.
%
While the light jet mistag probability is small, we find that
in general the $2b2j$ and $4j$ backgrounds cannot be neglected because
of their large cross-sections and enhancement from combinatorics, that
increase their contribution as compared to the naive estimate.
